Measuring Political Freedom Around the World

### 2020-11-11 slides.Rmd
updated slides

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
  labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_light(base_size = 30)

```

@@

$$
\tiny
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$

```{r}
broom::tidy(model_df5) %>% 
  kable()
```
---
class: animated, fadeIn, center
$$
\tiny
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kable() %>% 
  row_spec(4, bold = T, color = "white", background = "#D7261E")
```

@@

class: center, top
<font size="1">
```{r results='asis',out.width='25%', fig.align='center',}
stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
                     title = "Regression Results", 
                     covariate.labels = c(),header = FALSE,
single.row=FALSE,column.sep.width = "-15pt")
```

>>>>

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
  labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_light(base_size = 30)
```

@@

$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$

```{r}
broom::tidy(model_df5) %>% 
  kable()
```
---
class: center
$$
\small
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kable() %>% 
  row_spec(4, bold = T, color = "white", background = "#D7261E")
```

@@

<font size="-10">
```{r results='asis'}
stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
                     title = "Regression Results", 
                     covariate.labels = c(),
                     header = FALSE,
                     single.row = FALSE)
```
